{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2021-11-24 pheno.tex

The main MSSM contributions are expected to come from chargino--stop\footnote{We usually expect higher generation off-diagonal soft terms to be larger due to RGE running controlled by Yukawa couplings.} and charged Higgs--top loops, as shown in Figs.~\ref{btosdiags} c) and d), respectively. However,  there is little room for effects from supersymmetry since the current experimental world average is ${\rm Br}(B\to X_s\gamma)=(3.55\pm 0.26)\cdot 10^{-4}$ (PDG 2010). This means that either the charged Higgs is heavy enough and the stop-scharm soft mass term small enough not to contribute significantly, or that there are cancellations between the two contributions. This is both an example of a process that puts significant constraints on off-diagonal soft terms, and a process that is important in constraining the possible values of the charged Higgs mass.

>>>>

The main MSSM contributions are expected to come from chargino--stop\footnote{We usually expect higher generation off-diagonal soft terms to be larger due to RGE running controlled by Yukawa couplings.} and charged Higgs--top loops, as shown in Figs.~\ref{btosdiags} c) and d), respectively. However,  there is little room for effects from supersymmetry since the current experimental world average is ${\rm Br}(B\to X_s\gamma)=(3.32\pm 0.15)\cdot 10^{-4}$ (PDG 2010). This means that either the charged Higgs is heavy enough and the stop-scharm soft mass term small enough not to contribute significantly, or that there are cancellations between the two contributions. This is both an example of a process that puts significant constraints on off-diagonal soft terms, and a process that is important in constraining the possible values of the charged Higgs mass.
